\documentclass[11pt, a4paper]{awesome-cv}
% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
\colorlet{awesome}{awesome-red}

% Uncomment if you would like to specify your own color
% \colorlet{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------

% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Kevin}{TONGUE}
\position{5th year student{\enskip\cdotp\enskip}Mechanical engineering}
\address{65, Rue Jean Parot , Saint-Étienne,France}

\mobile{(+33) 06 98 06 37 69}
\email{tonguekevin00@gmail.com}
% \homepage{www.posquit0.com}
\github{tittank1802}
\linkedin{tongue-kevin-52b100330}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{medium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}
% \quote{``Be the change that you want to see in the world."}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Kevin TONGUE~~~·~~~Curriculum Vitae}
  {\thepage}

%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%-------------------------------------------------------------------------------

\cvsection{Education}

\begin{cventries}
\cventry
    {M2 in Mechanical Engineering \textbullet{} Design and Numerical Simulation} % Degree
    {Centrale Lyon-ENISE} % Institution
    {Saint-Étienne, France} % Location
    {2026} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Pursuing a Master's degree in mechanical engineering with a focus on design and advanced numerical simulation techniques, including multi-physics modeling.}
      \end{cvitems}
    }
\cventry
    {M2 in Numerical Solid Mechanics} % Degree
    {Centrale Lyon-ENISE} % Institution
    {Saint-Étienne, France} % Location
    {2026} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Pursuing a Master's degree in Numerical Solid Mechanics, emphasizing computational methods for solving partial differential equations in solid mechanics and heat/mass transfer problems.}
        \item {Completed the MIAM (Méthodes d'Intelligence Artificielle pour la Physique) module, acquiring expertise in physics-informed neural networks (PINNs) for modeling physical phenomena such as coupled heat and diffusion processes.}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Skills}

\begin{cvskills}
\cvskill
    {Programming} % Category
    {Python (including TensorFlow/PyTorch for neural networks), MATLAB, C, C++, C\#, Java, Fortran, LaTeX} % Skills
\cvskill
    {CAD \& Simulation} % Category
    {SolidWorks, CATIA, 3DEXPERIENCE, PLM} % Skills
\cvskill
    {Office \& Tools} % Category
    {Word, Excel, PowerPoint} % Skills
\cvskill
    {Soft Skills} % Category
    {Problem-Solving, Flexibility, Commitment, Team Collaboration, Team Player} % Skills
\cvskill
    {Languages} % Category
    {French (Native), English (Fluent), German (Intermediate)} % Skills
\end{cvskills}

\cvsection{Experience}

\begin{cventries}
\cventry
    {Fatigue Analysis of Industrial Structures Subjected to Complex Loads} % Affiliation/role
    {Centrale Lyon ENISE} % Organisation
    {Saint-Étienne, France} % Location
    {Oct. 2025 -- Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Testing and validation of the non-regression of the numerical method of Agard et al. for the optimization of the Dang Van method based on the determination of critical planes, applying advanced numerical simulation techniques.}
      \end{cvitems}
    }
\cventry
    {Microstructure Partitioning Model (Python)} % Affiliation/role
    {École des Mines de Saint-Étienne} % Organisation
    {Saint-Étienne, France} % Location
    {Feb. 2025 -- June 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a Python-based model for partitioning microstructures to analyze material properties, leveraging numerical methods for material science simulations.}
      \end{cvitems}
    }
\cventry
    {Library Management Web Application (Symfony, PHP)} % Affiliation/role
    {École des Mines de Saint-Étienne} % Organisation
    {Saint-Étienne, France} % Location
    {Feb. 2025 -- June 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a web application for library management using Symfony and PHP, demonstrating software development skills applicable to simulation tools.}
      \end{cvitems}
    }
\cventry
    {Design of a Food Industry Lifting Trolley} % Affiliation/role
    {Centrale Lyon ENISE} % Organisation
    {Saint-Étienne, France} % Location
    {Mar. 2025 -- June 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered a lifting trolley for the food industry, focusing on ergonomic and safety aspects using CAD and numerical analysis.}
      \end{cvitems}
    }
\cventry
    {Design of a Gardening Assistance Cart} % Affiliation/role
    {Centrale Lyon ENISE} % Organisation
    {Saint-Étienne, France} % Location
    {Sep. 2024 -- Dec. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a gardening assistance cart to improve user comfort and efficiency, incorporating mechanical design and simulation.}
      \end{cvitems}
    }
\cventry
    {Design and Manufacturing of a 3-Axis CNC Machine} % Affiliation/role
    {Fablab ENSPY} % Organisation
    {Yaoundé, Cameroon} % Location
    {Sep. 2023 -- Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built a 3-axis CNC machine for prototyping and educational purposes, applying mechanical engineering principles.}
      \end{cvitems}
    }
\cventry
    {Engineer Internship in Maintenance of Newspaper Printing Machines} % Affiliation/role
    {SOPECAM (Société de Presse et d'Éditions du Cameroun)} % Organisation
    {Yaoundé, Cameroon} % Location
    {May 2024 -- Sep. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Determined the causes of pump failures on the KBA machine and proposed methods to prevent these failures.}
        \item {Designed a software package for managing the preventive maintenance of the pump, using programming for reliability analysis.}
      \end{cvitems}
    }
\cventry
    {Technician Internship at Fablab of ENSPY} % Affiliation/role
    {ENSPY (École Nationale Supérieure Polytechnique Yaoundé)} % Organisation
    {Yaoundé, Cameroon} % Location
    {May 2023 -- Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed causes of equipment failures and proposed preventive measures, gaining hands-on experience in mechanical systems maintenance.}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Extracurricular Activities}

\begin{cventries}
\cventry
    {Core Member, Robotic Group} % Affiliation/role
    {ENISE} % Organisation
    {} % Location
    {Nov. 2024 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gained expertise in designing electronic devices and participated in multiple competitions, enhancing problem-solving in mechatronics.}
      \end{cvitems}
    }
\cventry
    {Member, Social Group} % Affiliation/role
    {ENISE} % Organisation
    {} % Location
    {Sep. 2024 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed skills in team collaboration and networking.}
      \end{cvitems}
    }
\cventry
    {Member, Football Group} % Affiliation/role
    {ENISE} % Organisation
    {} % Location
    {Sep. 2024 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Played in a team and took charge of responsibilities, fostering leadership and teamwork.}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Honors \& Awards}

\begin{cvhonors}
\cvhonor
    {MATLAB Onramp, Simulink Onramp} % Name
    {MathWorks Online Training} % Organization
    {2025} % Date
    {}
\cvhonor
    {MATLAB Power System Onramp, Computer Vision Onramp} % Name
    {MathWorks Online Training} % Organization
    {2025} % Date
    {}
\cvhonor
    {SOLIDWORKS 3D CAD for Education, SOLIDWORKS xDesign for Education} % Name
    {Coursera Online} % Organization
    {2025} % Date
    {}
\cvhonor
    {Google Advanced Data Analytics} % Name
    {Coursera Online} % Organization
    {2024} % Date
    {}
\cvhonor
    {IBM Data Analyst} % Name
    {Coursera Online} % Organization
    {2024} % Date
    {}
\end{cvhonors}

%-------------------------------------------------------------------------------
\end{document}